Topology and experimental distinguishability

### 2017-08-08 Articles/TopologyAndExperimentalDistinguishability/article.tex
Finished proof for basis-to-basis topology

\begin{proof}
	The collection $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is defined to be the topology generated by the sets $V(U_X,U_Y)$, so it contains the empty set, all of $C(X,Y)$, and is closed under arbitrary union and finite intersection by definition.
\end{proof}

>>>>

\begin{proof}
	The collection $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is defined to be the topology generated by the sets $V(U_X,U_Y)$, so it contains the empty set and is closed under arbitrary union and finite intersection by definition. To see why these sets contain every continuous function, let $f\in C(X,Y)$. Then for any $U_Y\in \mathcal{B}_Y$, we can find some $U_X\in \mathcal{B}_X$ such that $U_X\subseteq f^{-1}(U_Y)$. Then $f\in V(U_X,U_Y)$.
\end{proof}
